# rutils <a href = "https://danielvartan.github.io/brandr/"><img src = "man/figures/logo.png" align="right" width="120" /></a>

<!-- quarto render -->

```{r}
#| label: setup
#| include: false

library(rutils)

library(badger)
library(beepr)
library(cffr)
library(codemetar)
library(groomr) # https://github.com/danielvartan/groomr
library(here)
library(rutils) # https://github.com/danielvartan/rutils
```

<!-- badges: start -->
```{r}
#| echo: false
#| output: asis

cat(
  badger::badge_repostatus("active"),
  badger::badge_github_actions(action = "R-CMD-check.yaml"),
  badger::badge_codecov() |> rutils::shush(),
  badger::badge_license(
    "MIT",
    "green",
    url = "https://choosealicense.com/licenses/mit/"
  )
)
```
<!-- badges: end -->

## Overview

`rutils` is an R package that I (Daniel Vartanian) use to store and organize my utility functions until they are ready to be moved to their own package.

This package is primarily intended for personal use, but you are welcome to use it if you find it helpful. Please note that not all functions are exported or documented. Access the source code to see them all.

> If you find this project useful, please consider giving it a star! &nbsp; [![GitHub repo stars](https://img.shields.io/github/stars/danielvartan/rutils)](https://github.com/danielvartan/rutils/)

## Installation

You can install `rutils` using the [`remotes`](https://github.com/r-lib/remotes) package:

``` {r}
#| eval: false

remotes::install_github("danielvartan/rutils")
```

## License

```{r}
#| echo: false
#| output: asis

cat(
  badger::badge_license(
    "MIT",
    "green",
    url = "https://choosealicense.com/licenses/mit/"
  )
)
```

`rutils` code is released under the [MIT license](https://opensource.org/license/mit/). This means you can use, modify, and distribute the code as long as you include the original license in any copies of the software that you distribute.
